The watershed transform in ITK - discussion and new developments

### 2006-04-23 article/Article.tex
add image from current itk watershed
darcs-hash:20060423230435-2fc9d-1951809248b9364c0ddbf1f99feff5071c99261c.gz

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=4]{threshold}}
\subfigure[No minima threshold]{\includegraphics[scale=4]{threshold00-rgb}}
\subfigure[Minima threshold = 10]{\includegraphics[scale=4]{threshold10-rgb}}
\subfigure[Minima threshold = 20]{\includegraphics[scale=4]{threshold20-rgb}}
\subfigure[Minima threshold = 30 and Minima threshold = 40]{\includegraphics[scale=4]{threshold30-rgb}}
\subfigure[Minima threshold = 50]{\includegraphics[scale=4]{threshold50-rgb}}
\subfigure[markers]{\includegraphics[scale=4]{threshold-markers}}
\subfigure[Watershed from markers]{\includegraphics[scale=4]{threshold-markersMf-rgb}}
\caption{Different results of watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical waterhsed oversegmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image. All the watersheds were performed with $MarkWatershed = true$ and $FullyConnected = false$.}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\subfigure[]{\includegraphics[scale=10]{pass-values}}
\subfigure[]{\includegraphics[scale=10]{pass-values-mf-rgb}}
\subfigure[]{\includegraphics[scale=10]{pass-values-mF-rgb}}
\subfigure[]{\includegraphics[scale=10]{pass-values-Mf-rgb}}
\subfigure[]{\includegraphics[scale=10]{pass-values-MF-rgb}}
\subfigure[]{\includegraphics[scale=10]{pass-values}}

\subfigure[]{\includegraphics[scale=4]{plateau}}
\subfigure[]{\includegraphics[scale=4]{plateau-mf-rgb}}
\subfigure[]{\includegraphics[scale=4]{plateau-mF-rgb}}
\subfigure[]{\includegraphics[scale=4]{plateau-Mf-rgb}}
\subfigure[]{\includegraphics[scale=4]{plateau-MF-rgb}}
\subfigure[]{\includegraphics[scale=4]{plateau}}

\subfigure[]{\includegraphics[scale=10]{thick-lines}}
\subfigure[]{\includegraphics[scale=10]{thick-lines-mf-rgb}}
\subfigure[]{\includegraphics[scale=10]{thick-lines-mF-rgb}}
\subfigure[]{\includegraphics[scale=10]{thick-lines-Mf-rgb}}
\subfigure[]{\includegraphics[scale=10]{thick-lines-MF-rgb}}
\subfigure[]{\includegraphics[scale=10]{thick-lines}}

\subfigure[]{\includegraphics[scale=6]{button-hole}}
\subfigure[]{\includegraphics[scale=6]{button-hole-mf-rgb}}
\subfigure[]{\includegraphics[scale=6]{button-hole-mF-rgb}}
\subfigure[]{\includegraphics[scale=6]{button-hole-Mf-rgb}}
\subfigure[]{\includegraphics[scale=6]{button-hole-MF-rgb}}
\subfigure[]{\includegraphics[scale=6]{button-hole}}

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[]{\includegraphics[scale=0.7]{cthead1}}
\subfigure[]{\includegraphics[scale=0.7]{cthead1-markers}}
\subfigure[]{\includegraphics[scale=0.7]{cthead1mf-rgb}}
\subfigure[]{\includegraphics[scale=0.7]{cthead1mF-rgb}}
\subfigure[]{\includegraphics[scale=0.7]{cthead1Mf-rgb}}
\subfigure[]{\includegraphics[scale=0.7]{cthead1MF-rgb}}
\caption{}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=4]{threshold}}
\subfigure[No minima threshold]{\includegraphics[scale=4]{threshold00-rgb}}
\subfigure[Minima threshold = 10]{\includegraphics[scale=4]{threshold10-rgb}}
\subfigure[Minima threshold = 20]{\includegraphics[scale=4]{threshold20-rgb}}
\subfigure[Minima threshold = 30 and Minima threshold = 40]{\includegraphics[scale=4]{threshold30-rgb}}
\subfigure[Minima threshold = 50]{\includegraphics[scale=4]{threshold50-rgb}}
\subfigure[markers]{\includegraphics[scale=4]{threshold-markers}}
\subfigure[Watershed from markers]{\includegraphics[scale=4]{threshold-markersMf-rgb}}
\caption{Different results of watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image. All the watersheds were performed with $MarkWatershed = true$ and $FullyConnected = false$.}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=4]{threshold}}
\subfigure[No minima threshold]{\includegraphics[scale=4]{threshold00-itk-rgb}}
\subfigure[Minima threshold = 10]{\includegraphics[scale=4]{threshold10-itk-rgb}}
% \subfigure[Minima threshold = 20]{\includegraphics[scale=4]{threshold20-itk-rgb}}
\subfigure[Minima threshold = 40]{\includegraphics[scale=4]{threshold40-itk-rgb}}
\subfigure[Minima threshold = 63]{\includegraphics[scale=4]{threshold63-itk-rgb}}
\subfigure[Minima threshold = 65]{\includegraphics[scale=4]{threshold65-itk-rgb}}
\subfigure[markers]{\includegraphics[scale=4]{threshold-markers}}
\subfigure[Watershed from markers]{\includegraphics[scale=4]{threshold-markers-itk-rgb}}
\caption{Different results of watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image..}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\subfigure[]{\includegraphics[scale=10]{pass-values}}
\subfigure[]{\includegraphics[scale=10]{pass-values-mf-rgb}}
\subfigure[]{\includegraphics[scale=10]{pass-values-mF-rgb}}
\subfigure[]{\includegraphics[scale=10]{pass-values-Mf-rgb}}
\subfigure[]{\includegraphics[scale=10]{pass-values-MF-rgb}}
\subfigure[]{\includegraphics[scale=10]{pass-values-itk-rgb}}

\subfigure[]{\includegraphics[scale=4]{plateau}}
\subfigure[]{\includegraphics[scale=4]{plateau-mf-rgb}}
\subfigure[]{\includegraphics[scale=4]{plateau-mF-rgb}}
\subfigure[]{\includegraphics[scale=4]{plateau-Mf-rgb}}
\subfigure[]{\includegraphics[scale=4]{plateau-MF-rgb}}
\subfigure[]{\includegraphics[scale=4]{plateau-itk-rgb}}

\subfigure[]{\includegraphics[scale=10]{thick-lines}}
\subfigure[]{\includegraphics[scale=10]{thick-lines-mf-rgb}}
\subfigure[]{\includegraphics[scale=10]{thick-lines-mF-rgb}}
\subfigure[]{\includegraphics[scale=10]{thick-lines-Mf-rgb}}
\subfigure[]{\includegraphics[scale=10]{thick-lines-MF-rgb}}
\subfigure[]{\includegraphics[scale=10]{thick-lines-itk-rgb}}

\subfigure[]{\includegraphics[scale=6]{button-hole}}
\subfigure[]{\includegraphics[scale=6]{button-hole-mf-rgb}}
\subfigure[]{\includegraphics[scale=6]{button-hole-mF-rgb}}
\subfigure[]{\includegraphics[scale=6]{button-hole-Mf-rgb}}
\subfigure[]{\includegraphics[scale=6]{button-hole-MF-rgb}}
\subfigure[]{\includegraphics[scale=6]{button-hole-itk-rgb}}

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[]{\includegraphics[scale=0.5]{cthead1}}
\subfigure[]{\includegraphics[scale=0.5]{cthead1-markers}}
\subfigure[]{\includegraphics[scale=0.5]{cthead1mf-rgb}}
\subfigure[]{\includegraphics[scale=0.5]{cthead1mF-rgb}}
\subfigure[]{\includegraphics[scale=0.5]{cthead1Mf-rgb}}
\subfigure[]{\includegraphics[scale=0.5]{cthead1MF-rgb}}
\subfigure[]{\includegraphics[scale=0.5]{cthead1itk-rgb}}
\caption{}
\end{center}
\end{figure}
